Wettability of Doped Two-Dimensional Materials

### 2017-02-22 writing/paper-Tian-gr-wetting.tex
Change style to achemso (ACS Nano)

% Created 2017-02-07 Tue 22:04
% Intended LaTeX compiler: pdflatex
\documentclass[aps,prl,reprint,groupedaddress,amsmath,amssymb, showpacs]{revtex4-1}
 \usepackage{minted}
 \usepackage{graphicx}
\usepackage{float}
\usepackage{xcolor}
\usepackage{fontspec}
\date{}
\title{}
\begin{document}

\title{A Multiscale View of the Doping-Induced Tunable Wettability on Two-Dimensional Materials}
\author{Tian Tian} 
  \affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\author{Elton J. G. Santos}
  \affiliation{School of Mathematics and Physics, Queen's University Belfast, United Kingdom}
  \affiliation{School of Chemistry and Chemical Engineering, Queen's University Belfast, United Kingdom}
\author{Shangchao Lin}
  \email{slin@eng.fsu.edu.}
  \affiliation{Department of Mechanical Engineering, Materials Science and Engineering Program, FAMU-FSU College of Engineering, Florida State University, Tallahassee, Florida 32310, United States}
\author{Chih-Jen Shih}
  \email{chih-jen.shih@chem.ethz.ch}
  \affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}

\date{\today}

\begin{abstract}
  The emergence of 2D-material-based liquid-phase devices calls for
  the need for understanding the wetting property at the
  2D-material-liquid interface, and particularly the doping-induced
  tuning of wetting properties. In this letter, we propose a
  multiscale view of the doping-induced tunable wettability of 2D
  materials, by combining the reorientation effect of water molecules
  estimated by MD simulation, and the electrowetting effect calculated
  by continuum model. We reveal the electrostatic nature of the
  doping-induced wettability under both scale. We further evaluate the
  recent finding of doping-induced wettability tuning of graphene with
  the proposed model, by considering incomplete surface coverage of 2D
  materials. We find that minor surface incompleteness can cause great
  discrepancy in the measured value of interfacial wettability, requiring
  extreme care for interpreting the experimental results. In
  addition, we prove that a 2D material with higher density of states
  can essentially reduce the gating voltage in a 2D-material-based
  electrowetting device, and rank the tunability of the 2D materials
  as: MoTe$_{2}$ > MoS$_{2}$ > WTe$_{2}$ > WS$_{2}$ > germanene > silicene >
  graphene. Our multiscale analysis provides a comprehensive view of
  the wettability of 2D material interface, and we believe operational
  2D-material-based liquid manipulating devices will be facilitate by
  the principles presented in this letter.
\end{abstract}
\maketitle

>>>>

% Created 2017-02-22 Wed 13:07
% Intended LaTeX compiler: pdflatex
\documentclass[journal=ancac3,manuscript=article,email=true]{achemso}
 \usepackage{minted}
 \usepackage{graphicx}
\usepackage{float}
\usepackage{xcolor}
\usepackage{fontspec}
\author{Tian Tian}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\author{Elton J. G. Santos}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, United Kingdom}
\affiliation{School of Chemistry and Chemical Engineering, Queen's University Belfast, United Kingdom}
\author{Shangchao Lin}
\email{slin@eng.fsu.edu.}
\affiliation{Department of Mechanical Engineering, Materials Science and Engineering Program, FAMU-FSU College of Engineering, Florida State University, Tallahassee, Florida 32310, United States}
\author{Chih-Jen Shih}
\email{chih-jen.shih@chem.ethz.ch}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\date{}
\title{Wettability of Doped Two-Dimensional Materials}
\begin{document}

\newpage{}
\begin{abstract}
  The emergence of 2D-material-based liquid-phase devices calls for
  the need for understanding the wetting property at the
  2D-material-liquid interface, and particularly the doping-induced
  tuning of wetting properties. In this letter, we propose a
  multiscale view of the doping-induced tunable wettability of 2D
  materials, by combining the reorientation effect of water molecules
  estimated by MD simulation, and the electrowetting effect calculated
  by continuum model. We reveal the electrostatic nature of the
  doping-induced wettability under both scale. We further evaluate the
  recent finding of doping-induced wettability tuning of graphene with
  the proposed model, by considering incomplete surface coverage of 2D
  materials. We find that minor surface incompleteness can cause great
  discrepancy in the measured value of interfacial wettability, requiring
  extreme care for interpreting the experimental results. In
  addition, we prove that a 2D material with higher density of states
  can essentially reduce the gating voltage in a 2D-material-based
  electrowetting device, and rank the tunability of the 2D materials
  as: MoTe$_{2}$ > MoS$_{2}$ > WTe$_{2}$ > WS$_{2}$ > germanene > silicene >
  graphene. Our multiscale analysis provides a comprehensive view of
  the wettability of 2D material interface, and we believe operational
  2D-material-based liquid manipulating devices will be facilitate by
  the principles presented in this letter.
\end{abstract}
\maketitle
